---
title: "Portfolio Manager"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    source_code: embed
runtime: shiny
---

```{r setup, include = F}
library("data.table")
library("dplyr")
library("ggplot2")
library("plotly")
library("tidyverse")
library("flexdashboard")
library("shiny")
library("DT")

# - pins Board Configuration
board_nm <- "Portfolio Management"
pins::board_register_local(name = board_nm)

# - Default List
ticker_list <- 
  pins::pin_get("md_stock_prices", board_nm) %>% 
  dplyr::pull(ticker) %>% 
  unique()

# - Download Data
md_stock_prices <- 
  pins::pin_get("md_stock_prices", board_nm) %>% 
  as.data.frame()

# - Editable Table Functions
modDtUi <- function(id){
  ns = NS(id)
  DT::dataTableOutput(ns('x1'))
}

modDt <-  function(input, output, session, data){
  output$x1 <- 
    DT::renderDataTable(data, 
                        selection = "none",
                        extensions = "Buttons",
                        editable = list(target = "all",
                                        disable = 
                                          list(columns = 
                                                 c(1, 2, 3, 5, 6, 7))), 
                        server = TRUE, 
                        options = list(dom = "Blfrtip",
                                       buttons = c("copy", "csv", "excel"),
                                       scrollX = T,
                                       lengthMenu = list(c(5, 10, 20),
                                                         c(5, 10, 20))),
                        filter = "top", 
                        class = "cell-border stripe") 
  proxy <- dataTableProxy("x1", session = session)
  
  updatedData <- eventReactive(input$x1_cell_edit, {
    info = input$x1_cell_edit
    if (!is.null(info)) {
      str(info)
      data <<- DT::editData(data, info)
    }
    data
  }, ignoreNULL = FALSE)
  
  return(updatedData)
}
```

Patria Stocks
=======================================================================

Column {.sidebar data-width=200}
-----------------------------------------------------------------------

$~$

```{r}
actionButton(inputId = "patria_ticker_refresher", 
             label = "Refresh Ticker Names", 
             width = "100%")

renderText({
  upload_ticker_changes()
})

```

Column {.tabset}
-----------------------------------------------------------------------

### Stock List

```{r}
modDtUi("edit_ticker")
change_ticker <- 
  callModule(modDt, "edit_ticker", 
             data = pins::pin_get("MarginCP", board_nm) %>% 
               dplyr::left_join(., pins::pin_get("md_stock_prices", board_nm) %>% 
                                  dplyr::group_by(ticker) %>% 
                                  dplyr::summarise(`# Observations` = as.numeric(n())) %>% 
                                  as.data.frame(),
                                by = c("Adjusted Ticker" = "ticker")) %>%
               dplyr::mutate(`# Observations` = dplyr::if_else(is.na(`# Observations`), 0, `# Observations`)) %>% 
               as.data.frame())

# ----- Rewrite Table -----
saved_changes <- reactive({
  out_df <- change_ticker() %>% as.data.frame()
  
  return(out_df)
})

# ----- Save to Database -----
upload_ticker_changes <- eventReactive(input$patria_ticker_refresher, {
  
  saved_df <- 
    saved_changes() %>%
    dplyr::select(-`# Observations`) %>% 
    as.data.frame() %>% 
    pins::pin(x = ., name = "MarginCP", board = board_nm)
  
  return("Succesfully Uploaded!")
})
```

### Stocks by Country

```{r}
stocks_by_country <-
  pins::pin_get("MarginCP", board_nm) %>% 
  dplyr::group_by(`Země`) %>% 
  dplyr::summarise(`Number of Stocks` = n()) %>% 
  dplyr::mutate(`is Downloaded` = "All Stocks") %>% 
  
  rbind(., pins::pin_get("MarginCP", board_nm) %>% 
          dplyr::filter(`Adjusted Ticker` %in% c(pins::pin_get("md_stock_prices", board_nm) %>% 
                                                   dplyr::select(ticker) %>% 
                                                   distinct() %>% 
                                                   as.data.frame() %>% 
                                                   dplyr::pull(ticker))) %>% 
          dplyr::group_by(`Země`) %>% 
          dplyr::summarise(`Number of Stocks` = n()) %>% 
          dplyr::mutate(`is Downloaded` = "Downloaded") %>% 
          as.data.frame()) %>% 
  as.data.frame() %>% 
  
  ggplot(data = .) +
  geom_bar(aes(x = `Země`, y = `Number of Stocks`, fill = `is Downloaded`), 
           stat = "identity", position = "dodge") +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust = 1), 
        legend.title = element_blank())

ggplotly(stocks_by_country)
```

Patria Costs
=======================================================================

ETL
=======================================================================

Column {.sidebar data-width=300}
-----------------------------------------------------------------------

$~$

**Refresh Data**

```{r}
actionButton(inputId = "run_download", label = "Run Data Download", width = "100%")

# - Establish RStudio job
download_data_plt <-
  eventReactive(input$run_download, {
    
    if (input$run_download) {
      
      rstudioapi::jobRunScript(path = "C:/Users/peter.tomko/OneDrive - Publicis Groupe/Desktop/ds_projects/portfolio_management/0 data download/stock price download.R", 
                               name = "Data Download", 
                               workingDir = "C:/Users/peter.tomko/OneDrive - Publicis Groupe/Desktop/ds_projects/portfolio_management")
    }
  })

# - Rendering of Objects
shiny::renderPrint({
  download_data_plt()
})
```

$~$

**Statistical Analysis**

Using **Run ADF Analysis** and **Run Hurst Analysis** buttons, the analysis will be performed. Analysis are in the form of **.Rmd** documents stored in **./adhoc analysis**. The output will be loaded in **ADF Test & Hurst Exponent** bookmark.

```{r}
actionButton(inputId = "run_adf", label = "Run ADF Analysis", width = "100%")

# - Establish RStudio job
adf_analysis <-
  eventReactive(input$run_adf, {
    
    if (input$run_adf) {
      
      rstudioapi::jobRunScript(path = "C:/Users/peter.tomko/OneDrive - Publicis Groupe/Desktop/ds_projects/portfolio_management/adhoc analysis/runFiles/ADF.R", 
                               name = "ADF Test", 
                               workingDir = "C:/Users/peter.tomko/OneDrive - Publicis Groupe/Desktop/ds_projects/portfolio_management")
    }
  })

# - Rendering of Objects
shiny::renderPrint({
  adf_analysis()
})

```

```{r}
actionButton(inputId = "run_hurst", label = "Run Hurst Analysis", width = "100%")

# - Establish RStudio job
hurst_analysis <-
  eventReactive(input$run_hurst, {
    
    if (input$run_hurst) {
      
      rstudioapi::jobRunScript(path = "C:/Users/peter.tomko/OneDrive - Publicis Groupe/Desktop/ds_projects/portfolio_management/adhoc analysis/runFiles/Hurst.R", 
                               name = "Hurst Analysis", 
                               workingDir = "C:/Users/peter.tomko/OneDrive - Publicis Groupe/Desktop/ds_projects/portfolio_management")
    }
  })

# - Rendering of Objects
shiny::renderPrint({
  hurst_analysis()
})
```

Column {.tabset}
-----------------------------------------------------------------------

### Check Missing Tickers

```{r}
pins::pin_get("MarginCP", board_nm) %>% 
  as.data.frame() %>% 
  dplyr::filter(!(`Adjusted Ticker` %in% c(pins::pin_get("md_stock_prices", board_nm) %>% 
                                             dplyr::select(ticker) %>% 
                                             distinct() %>% 
                                             as.data.frame() %>% 
                                             dplyr::pull(ticker)))) %>% 
  as.data.frame() %>% 
  
  datatable(extensions = "Buttons",
            filter = "top",
            options = list(dom = "Blfrtip",
                           buttons = c("copy", "csv", "excel"),
                           scrollX = T,
                           lengthMenu = list(c(10, 25, 50, -1),
                                             c(10, 25, 50, "All"))))
```

### Check Latest Date of Download
```{r Latest Date of Download}
line_plt <-
  pins::pin_get("md_stock_prices", board_nm) %>% 
  dplyr::select(ticker, dt) %>% 
  distinct() %>% 
  dplyr::group_by(dt) %>% 
  dplyr::summarise(`# Observations` = n()) %>% 
  dplyr::rename(`Date` = dt) %>% 
  as.data.frame() %>% 
  
  ggplot(data = .) +
  geom_line(aes(x = Date, y = `# Observations`))

plotly::ggplotly(line_plt)
```

ADF Test & Hurst Exponent
=======================================================================

Column {.sidebar data-width=300}
-----------------------------------------------------------------------

The **good stock** is currently considered one that fulfill following conditions

- time series is identified as **Mean Reversion Process** on **1%** p-value using **ADF Test**

- time series is not identified as **Possible Random Walk** using **Hurst Exponent**

For more information have a look at **./adhoc analysis/ADF-test.html** and **./adhoc analysis/Stationary-Test-using-Hurst-Exponent.html**.

Column {.tabset}
-----------------------------------------------------------------------

### Predictability of Stocks
```{r}
stocks_selected <-
  pins::pin_get("adf_test_result", board_nm) %>% 
  dplyr::select(ticker, price_type, test_interpretation) %>% 
  dplyr::rename(adf_interpretation = test_interpretation) %>% 
  as.data.frame() %>% 
  
  left_join(., pins::pin_get("hurst_result", board_nm) %>% 
              dplyr::select(ticker, price_type, test_interpretation) %>% 
              dplyr::rename(hurst_interpretation = test_interpretation) %>% 
              as.data.frame()) %>% 
  
  left_join(., pins::pin_get("MarginCP", board_nm) %>% 
              dplyr::select(`Adjusted Ticker`, `Název`, `Země`) %>% 
              as.data.frame(), by = c("ticker" = "Adjusted Ticker")) %>% 
  as.data.frame() %>% 
  
  rowwise() %>% 
  dplyr::mutate(
    `ADF Good` = dplyr::if_else(!(adf_interpretation %in% c("Possible Random Walk", "Mean Reversion TS at 10%", "Mean Reversion TS at 5%")), 1, 0),
    `Hurst Good` = dplyr::if_else(hurst_interpretation != "Possible Random Walk", 1, 0),
  ) %>% 
  dplyr::group_by(ticker) %>% 
  dplyr::mutate(
    n_rows = n(),
    adf = sum(`ADF Good`),
    hurst = sum(`Hurst Good`),
  ) %>% 
  rowwise() %>% 
  dplyr::mutate(`is Good` = dplyr::if_else(n_rows == adf & n_rows == hurst, 1, 0)) %>% 
  as.data.frame() %>% 
  
  dplyr::rename(
    `ADF Result` = adf_interpretation,
    `Hurst Result` = hurst_interpretation,
    `Price Type` = price_type,
    `Company` = `Název`, 
    `Country` = `Země`
  ) %>% 
  dplyr::select(-n_rows, -adf, -hurst) %>% 
  dplyr::relocate(., `Country`, .after = `ticker`) %>% 
  dplyr::relocate(., `Company`, .after = `ticker`) %>% 
  as.data.frame()

stocks_selected %>% 
  datatable(extensions = "Buttons",
            filter = "top",
            options = list(dom = "Blfrtip",
                           buttons = c("copy", "csv", "excel"),
                           scrollX = T,
                           lengthMenu = list(c(10, 25, 50, -1),
                                             c(10, 25, 50, "All"))))
```

### Eliminated Stocks

```{r}
pins::pin_get("MarginCP", board_nm) %>% 
  as.data.frame() %>% 
  dplyr::filter(`Adjusted Ticker` %in% c(stocks_selected %>% 
                                           dplyr::filter(`is Good` < 1) %>% 
                                           dplyr::pull(ticker) %>% 
                                           unique())) %>% 
  as.data.frame() %>% 
  
  datatable(extensions = "Buttons",
            filter = "top",
            options = list(dom = "Blfrtip",
                           buttons = c("copy", "csv", "excel"),
                           scrollX = T,
                           lengthMenu = list(c(10, 25, 50, -1),
                                             c(10, 25, 50, "All"))))

```

### Selected Stocks

```{r}
pins::pin_get("MarginCP", board_nm) %>% 
  as.data.frame() %>% 
  dplyr::filter(`Adjusted Ticker` %in% c(stocks_selected %>% 
                                           dplyr::filter(`is Good` > 0) %>% 
                                           dplyr::pull(ticker) %>% 
                                           unique())) %>% 
  as.data.frame() %>% 
  
  datatable(extensions = "Buttons",
            filter = "top",
            options = list(dom = "Blfrtip",
                           buttons = c("copy", "csv", "excel"),
                           scrollX = T,
                           lengthMenu = list(c(10, 25, 50, -1),
                                             c(10, 25, 50, "All"))))

```

### Summary of Selected Stocks
```{r}
selected_stocks_summary_plt <-
  
  stocks_selected %>% 
  dplyr::select(ticker, Country, `is Good`) %>% 
  dplyr::distinct() %>% 
  dplyr::mutate(`is Good` = dplyr::if_else(`is Good` == 0, "Not suitable", "Suitable")) %>% 
  dplyr::group_by(Country, `is Good`) %>% 
  dplyr::summarise(
    `Number of Stocks` = n()
  ) %>% 
  as.data.frame() %>% 
  
  ggplot(data = .) +
  geom_bar(aes(x = Country, y = `Number of Stocks`, fill = `is Good`), 
           stat = "identity") +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust = 1), 
        legend.title = element_blank())

ggplotly(selected_stocks_summary_plt)
```

Stock Visualization
=======================================================================

Column {.sidebar data-width=200}
-----------------------------------------------------------------------

```{r}
selectInput("select_stock", 
            label = "Select Ticker", 
            choices = ticker_list[ticker_list %in% c(stocks_selected %>% 
                                                       dplyr::filter(`is Good` > 0) %>% 
                                                       dplyr::pull(ticker) %>% 
                                                       unique())], 
            multiple = F, 
            width = "100%")
```

Column
-----------------------------------------------------------------------

### OHLC Plot
```{r}
# - Establish Visualization
stock_viz <-
  eventReactive(input$select_stock, {
    
    stock_viz_plt <- 
      md_stock_prices %>% 
      dplyr::filter(ticker %in% c(input$select_stock)) %>% 
      as.data.frame() %>% 
      
      ggplot(data = .) +
      geom_line(aes(x = dt, y = open, col = "Open")) +
      geom_line(aes(x = dt, y = high, col = "High")) +
      geom_line(aes(x = dt, y = low, col = "Low")) +
      geom_line(aes(x = dt, y = close, col = "Close")) +
      
      xlab("Date") +
      ylab("Price") +
      theme(legend.title = element_blank())
    
    plotly::ggplotly(stock_viz_plt)
  })

# - Rendering Plot
plotly::renderPlotly({
  stock_viz()
})
```

### Distribution of Daily Returns
```{r}
# - Establish Visualization
stock_dist <-
  eventReactive(input$select_stock, {
    
    stock_dist_plt <- 
      md_stock_prices %>% 
      dplyr::filter(ticker %in% c(input$select_stock)) %>% 
      dplyr::arrange(dt) %>% 
      dplyr::mutate(`Daily Return` = (p_adjusted/dplyr::lag(p_adjusted, n = 1)) - 1) %>% 
      as.data.frame() %>% 
      
      ggplot(data = .) +
      geom_histogram(aes(`Daily Return`)) +
      ylab("")
    
    plotly::ggplotly(stock_dist_plt)
  })

# - Rendering Plot
plotly::renderPlotly({
  stock_dist()
})
```

Predictive Modelling
=======================================================================

Column {.sidebar data-width=300}
-----------------------------------------------------------------------

Here is the workflow visualized in the form of connected graph.

Column {.tabset}
-----------------------------------------------------------------------

### Features Engineering

### Backtesting Workflow

### Production Workflow

### Optimizer

### Margin Controller Visualization


Transaction db
=======================================================================

Actual Portfolio Performance
=======================================================================

Column {.sidebar data-width=200}
-----------------------------------------------------------------------

Column {.tabset}
-----------------------------------------------------------------------

### Portfolio vs. Benchmark Performance

### 

Help
=======================================================================

Inputs {.sidebar data-width=250}
-----------------------------------------------------------------------

$~$

Using **Download Backup Files** button, you can download all necessary files using which the main functionality of **Portfolio Manager App** might be transferred to other device.

```{r}
uiOutput("downloadUI")

output$downloadUI <- renderUI({
  downloadButton("downBtn", "Download Backup Files", style = "width:100%;")
})

output$downBtn <- downloadHandler(
  filename = function() {
    "portfolio_manager_backup.RData"
  },
  
  content = function(file) {
    
    MarginCP <- pins::pin_get("MarginCP", board_nm) %>% as.data.frame()
    md_stock_prices <- pins::pin_get("md_stock_prices", board_nm) %>% as.data.frame()
    
    save(MarginCP, md_stock_prices, file = file)
  }
)
```

About
=======================================================================

