---
title: "Modelling of Selected Stock Price"
subtitle: "Using Facebook Prophet Model"
output: html_document
---

# Setup
```{r setup, include = F, echo = T}
library("dplyr")
library("data.table")
library("prophet")
library("ggplot2")
library("tidymodels")

TRAIN_DT <- as.Date("2021-01-01")
board_nm <- "Portfolio Management"
```

## Load Modelling Data for `MasterCard`, i.e. `MA`
```{r Modelling Data}
# ----- Register Board -----
pins::board_register_local(name = board_nm)

# ----- Load Data -----
modelling_data <- 
  
  # - Download Data
  pins::pin_get("modelling_data_1.05_ret_10_wind", board_nm) %>% 
  as.data.frame() %>% 
  
  # create factor TARGET
  dplyr::mutate(
    target = as.factor(dplyr::if_else(target_10w > 0, "Over", "Under"))
  ) %>% 
  as.data.frame() %>% 
  
  # - split train/test
  dplyr::mutate(
    sample_type = dplyr::if_else(dt < TRAIN_DT, "Train", "Test")
  ) %>% 
  
  # - Remove columns
  dplyr::select(-open, -high, -low, -close, -p_adjusted, -volume) %>% 
  dplyr::mutate_if(is.character, as.factor) %>% 
  
  # - Select specific ticker
  dplyr::filter(ticker %in% c("MA")) %>% 
  as.data.frame()
```

## Load Raw Data for `MA`
```{r Raw Data}
raw_data <- 
  
  # - Download Data
  pins::pin_get("md_stock_prices", board_nm) %>% 
  as.data.frame() %>% 
  
  # - Select specific ticker
  dplyr::filter(ticker %in% c("MA") & volume > 0) %>% 
  
  # - Calculate Moving Averages
  dplyr::arrange(dt) %>%
  dplyr::mutate(
    ma20 = zoo::rollmean(close, k = 20, fill = NA, align = "right"),
    ma40 = zoo::rollmean(close, k = 40, fill = NA, align = "right"),
    ma60 = zoo::rollmean(close, k = 60, fill = NA, align = "right"),
    
    lag_ma20 = dplyr::lag(ma20, n = 1),
    lag_ma60 = dplyr::lag(ma60, n = 1),
  ) %>% 
  
  # - Train Test Prediction
  dplyr::arrange(desc(dt)) %>% 
  dplyr::mutate(sample = dplyr::if_else(row_number() > 40, "Train", "Test")) %>% 
  as.data.frame()
```

# General Visualization

## `MA 20`, `MA 40` & `MA 60`
```{r Moving Averages}
ma_plot <-
  ggplot(data = raw_data) +
  geom_line(aes(x = dt, y = close, col = "Close Price")) +
  geom_line(aes(x = dt, y = ma20, col = "MA 20")) +
  geom_line(aes(x = dt, y = ma40, col = "MA 40")) +
  geom_line(aes(x = dt, y = ma60, col = "MA 60")) +
  
  ggtitle("Close price with Moving averages") +
  theme(legend.title = element_blank())
plotly::ggplotly(ma_plot)
```

# Modelling using `prophet`

## Trend Changes
```{r}
trend_change <- 
  raw_data %>% 
  dplyr::filter(sample == "Train") %>% 
  na.omit() %>% 
  dplyr::mutate(bear_trend = dplyr::if_else(lag_ma20 > lag_ma60 & ma20 < ma60, 1, 0)) %>% 
  dplyr::mutate(bull_trend = dplyr::if_else(lag_ma20 < lag_ma60 & ma20 > ma60, 1, 0)) %>% 
  dplyr::filter(bear_trend + bull_trend > 0) %>% 
  dplyr::pull(dt)
```

## Develop Model for `MA 20`
```{r ma20 prophet}
ma20_prophet <- 
  prophet(df = raw_data %>%
            dplyr::rename(ds = dt,
                          y = ma20) %>% 
            dplyr::select(ds, y) %>% 
            as.data.frame(), 
          changepoints = trend_change,
          fit = T)
```

## Develop Model for `MA 40`
```{r ma40 prophet}
ma40_prophet <- 
  prophet(df = raw_data %>%
            dplyr::rename(ds = dt,
                          y = ma40) %>% 
            dplyr::select(ds, y) %>% 
            as.data.frame(), 
          changepoints = trend_change,
          fit = T)
```

## Develop Model for `MA 60`
```{r ma60 prophet}
ma60_prophet <- 
  prophet(df = raw_data %>%
            dplyr::rename(ds = dt,
                          y = ma60) %>% 
            dplyr::select(ds, y) %>% 
            as.data.frame(),
          changepoints = trend_change,
          fit = T)
```

## Develop Model for `close`
```{r close prophet}
close_prophet <- 
  prophet(df = raw_data %>%
            dplyr::rename(ds = dt,
                          y = close) %>% 
            dplyr::select(ds, y) %>% 
            as.data.frame(),
          changepoints = trend_change,
          fit = T)
```

## Develop Model for `open`
```{r open prophet}
open_prophet <- 
  prophet(df = raw_data %>%
            dplyr::rename(ds = dt,
                          y = open) %>% 
            dplyr::select(ds, y) %>% 
            as.data.frame(),
          changepoints = trend_change,
          fit = T)
```

## Develop Model for `high`
```{r high prophet}
high_prophet <- 
  prophet(df = raw_data %>%
            dplyr::rename(ds = dt,
                          y = high) %>% 
            dplyr::select(ds, y) %>% 
            as.data.frame(),
          changepoints = trend_change,
          fit = T)
```

## Develop Model for `low`
```{r low prophet}
low_prophet <- 
  prophet(df = raw_data %>%
            dplyr::rename(ds = dt,
                          y = low) %>% 
            dplyr::select(ds, y) %>% 
            as.data.frame(),
          changepoints = trend_change,
          fit = T)
```

## Combining Models
```{r Combining Models}
predeval_df <- 
  predict(ma20_prophet, 
          df = raw_data %>%
            dplyr::select(dt, close) %>% 
            dplyr::rename(ds = dt) %>% 
            dplyr::select(ds) %>%
            as.data.frame() %>% 
            rbind(., data.frame(ds = seq.Date(from = max(raw_data$dt) + 1, length.out = 60, by = 1)))) %>% 
  dplyr::select(ds, yhat) %>% 
  dplyr::rename(y_ma20 = yhat) %>% 
  as.data.frame() %>% 
  
  left_join(., predict(ma40_prophet, 
                       df = raw_data %>%
                         dplyr::select(dt, close) %>% 
                         dplyr::rename(ds = dt) %>% 
                         dplyr::select(ds) %>%
                         as.data.frame() %>% 
                         rbind(., data.frame(ds = seq.Date(from = max(raw_data$dt) + 1, length.out = 60, by = 1)))) %>% 
              dplyr::select(ds, yhat) %>% 
              dplyr::rename(y_ma40 = yhat) %>% 
              as.data.frame()) %>% 
  as.data.frame() %>% 
  
  left_join(., predict(ma60_prophet, 
                       df = raw_data %>%
                         dplyr::select(dt, close) %>% 
                         dplyr::rename(ds = dt) %>% 
                         dplyr::select(ds) %>%
                         as.data.frame() %>% 
                         rbind(., data.frame(ds = seq.Date(from = max(raw_data$dt) + 1, length.out = 60, by = 1)))) %>% 
              dplyr::select(ds, yhat) %>% 
              dplyr::rename(y_ma60 = yhat) %>% 
              as.data.frame()) %>% 
  as.data.frame() %>% 
  
  left_join(., predict(close_prophet, 
                       df = raw_data %>%
                         dplyr::select(dt, close) %>% 
                         dplyr::rename(ds = dt) %>% 
                         dplyr::select(ds) %>%
                         as.data.frame() %>% 
                         rbind(., data.frame(ds = seq.Date(from = max(raw_data$dt) + 1, length.out = 60, by = 1)))) %>% 
              dplyr::select(ds, yhat) %>% 
              dplyr::rename(y_close = yhat) %>% 
              as.data.frame()) %>% 
  as.data.frame() %>% 
  
  left_join(., predict(open_prophet, 
                       df = raw_data %>%
                         dplyr::select(dt, open) %>% 
                         dplyr::rename(ds = dt) %>% 
                         dplyr::select(ds) %>%
                         as.data.frame() %>% 
                         rbind(., data.frame(ds = seq.Date(from = max(raw_data$dt) + 1, length.out = 60, by = 1)))) %>% 
              dplyr::select(ds, yhat) %>% 
              dplyr::rename(y_open = yhat) %>% 
              as.data.frame()) %>% 
  as.data.frame() %>% 
  
  left_join(., predict(high_prophet, 
                       df = raw_data %>%
                         dplyr::select(dt, high) %>% 
                         dplyr::rename(ds = dt) %>% 
                         dplyr::select(ds) %>%
                         as.data.frame() %>% 
                         rbind(., data.frame(ds = seq.Date(from = max(raw_data$dt) + 1, length.out = 60, by = 1)))) %>% 
              dplyr::select(ds, yhat) %>% 
              dplyr::rename(y_high = yhat) %>% 
              as.data.frame()) %>% 
  as.data.frame() %>% 
  
  left_join(., predict(low_prophet, 
                       df = raw_data %>%
                         dplyr::select(dt, low) %>% 
                         dplyr::rename(ds = dt) %>% 
                         dplyr::select(ds) %>%
                         as.data.frame() %>% 
                         rbind(., data.frame(ds = seq.Date(from = max(raw_data$dt) + 1, length.out = 60, by = 1)))) %>% 
              dplyr::select(ds, yhat) %>% 
              dplyr::rename(y_low = yhat) %>% 
              as.data.frame()) %>% 
  as.data.frame() %>% 
  
  left_join(., raw_data %>%
              dplyr::select(dt, close, sample) %>% 
              dplyr::rename(ds = dt,
                            y = close) %>% 
              dplyr::arrange(desc(ds)) %>%
              as.data.frame()) %>% 
  as.data.frame()
```

# Prediction Performance
```{r Performance}
predeval_df %>% 
  tidyr::gather(., "model", "pred_val", -ds, -y, -sample) %>% 
  na.omit() %>% 
  dplyr::group_by(model) %>% 
  dplyr::summarise(
    rmse = rmse_vec(y, pred_val, na_rm = T),
    mae = mae_vec(y, pred_val, na_rm = T),
    mape = mape_vec(y, pred_val, na_rm = T),
  ) %>% 
  as.data.frame() %>% 
  DT::datatable(extensions = "Buttons",
                filter = "top",
                options = list(dom = "Blfrtip",
                               buttons = c("copy", "csv", "excel"),
                               lengthMenu = list(c(10, 25, 50, -1),
                                                 c(10, 25, 50, "All"))))

```

# Prediction of returns for upcoming `X` days
```{r Returns}

predeval_df %>% 
  dplyr::filter(is.na(sample)) %>% 
  dplyr::select(-y, -sample) %>% 
  tidyr::gather(., "model", "pred_val", -ds) %>% 
  dplyr::mutate(
    last_close = predeval_df %>% 
      na.omit() %>% 
      dplyr::arrange(desc(ds)) %>% 
      dplyr::slice(1) %>% 
      pull(y)) %>% 
  tidyr::crossing(., data.frame("days_window" = c(20, 40, 60))) %>% 
  as.data.frame() %>% 
  
  dplyr::group_by(model, days_window) %>% 
  dplyr::arrange(ds) %>% 
  dplyr::mutate(rownum = dplyr::if_else(row_number() <= days_window, 1, 0)) %>% 
  as.data.frame() %>% 
  
  dplyr::filter(rownum == 1) %>% 
  dplyr::select(-rownum) %>% 
  as.data.frame() %>% 
  
  dplyr::group_by(model, days_window) %>% 
  dplyr::summarise(
    avg_ret = mean((pred_val - last_close)/last_close),
    min_ret = min((pred_val - last_close)/last_close),
    max_ret = max((pred_val - last_close)/last_close),
    sd_ret = sd((pred_val - last_close)/last_close),
  ) %>% 
  as.data.frame() %>% 
  DT::datatable(extensions = "Buttons",
                filter = "top",
                options = list(dom = "Blfrtip",
                               buttons = c("copy", "csv", "excel"),
                               lengthMenu = list(c(10, 25, 50, -1),
                                                 c(10, 25, 50, "All"))))

predeval_df %>% 
  # dplyr::filter(is.na(sample)) %>%
  dplyr::select(y_close, y_ma20, y_ma40, y_ma60) %>% 
  as.data.frame() %>% 
  cor()

```